{\sc underworlds}: Cascading Situation Assessment for Robots

### 2018-01-24 paper.tex
Slightly better example of uwds client

\uwds currently offers such a high-level client library for Python only (a C++
library is under development).  Listing~\ref{lst|pythonapi} gives a complete
example of an \uwds client performing simple filtering: the client continuously
listens for changes in an input world, removes some objects (in this case, items
whose name contain the string ``{\tt wall}''), and forwards all other changes to
an output world, effectively making the output world a copy of the input world
with all walls removed.

@@

# by default, connect to the server on localhost
with underworlds.Context("walls_filter") as ctx:

@@

        for node in in_world.scene.nodes:
            if("wall" not in node.name):
                out_world.scene.nodes.update(node)

\end{pythoncode}
    \caption{Example of a simple yet complete \uwds filter, written in Python:
    the client connects to the \uwds network, walks through the scene graph of
    world {\tt example\_in}, filters out some objects, and publishes the
    remaining objects in the world {\tt example\_out}.}

>>>>

\uwds currently offers such a high-level client library for Python only (a C++
library is under development).  Listing~\ref{lst|pythonapi} gives a complete
example of an \uwds client performing simple filtering: the client continuously
listens for changes in an input world, removes some objects (in this case, items
whose volume is below a threshold), and forwards all other changes to
an output world, effectively making the output world a copy of the input world
with all smaller objects removed.

@@

# by default, connect to the server on localhost
with underworlds.Context("small_object_filter") as ctx:

@@

        for node in in_world.scene.nodes:
            if node.volume > THRESHOLD:
                out_world.scene.nodes.update(node)

\end{pythoncode}
    \caption{Example of a simple yet complete \uwds filter, written in Python:
    the client connects to the \uwds network, blocks until the world {\tt
    example\_in} changes, and only propagate nodes that match the condition to
    the world {\tt example\_out}.}
